How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-14 docs/PhysicsPaper/Referee Reports/Ref 1 Response/Ref1.tex
NM

Great question. This is an aspect of the simulation that we regarded as too detailed to fully explain in this manuscript, but it is an interesting aspect that we are happy to explain here. In essence, we use a simulated annealing procedure to initialize the configuration of circular bodies. We first determine the distribution of circle radii by straightforward sampling (we use a Chi distribution, but this choice is arbitrary) and by using the porosity that is specified. Second, we randomly assign the circle centers; many of the circles will overlap (unless we are incredibly lucky). Next, we specify fictitious forces that act to repel overlapping bodies and also repel bodies from the domain walls. In addition, the force acting on each body has a stochastic component with magnitude, or `temperature', that decreases over the course of the initialization routine. Hence, early in the initialization routine, the temperature is high and the random component is large compared to the deterministic forces, but at later stages, the temperature is low and the random component tends to zero. This algorithm allows the bodies to jump around substantially to explore different configurations and eventually converge to a configuration in which none overlap. Naturally, there are limitations to such an initialization algorithm. For example, there exists thresholds for the solid area fraction (that depend on the radius distribution) above which no circle packing is possible.
\end{document}

>>>>

Great question. This is an aspect of the simulation that we had regarded as too detailed to fully explain in this manuscript, but it is an interesting aspect that we are happy to explain here. In essence, we use a simulated annealing procedure to initialize the configuration of circular bodies. We first determine the distribution of circle radii by straightforward sampling (we use a Chi distribution, but this choice is arbitrary) and by using the porosity that is specified. Second, we randomly assign the circle centers; many of the circles will overlap (unless we are incredibly lucky). Next, we specify fictitious forces that act to repel overlapping bodies and also repel bodies from the domain walls. In addition, the force acting on each body has a stochastic component with magnitude, or `temperature', that decreases over the course of the initialization routine. Hence, early in the initialization routine, the temperature is high and the random component is large compared to the deterministic forces, but at later stages, the temperature is low and the random component tends to zero. This algorithm allows the bodies to jump around substantially to explore different configurations and eventually converge to a configuration in which none overlap. Naturally, there are limitations to such an initialization algorithm. For example, there exists thresholds for the solid area fraction (that depend on the radius distribution) above which no circle packing is possible.

We have added a brief explanation of this initialization algorithm to the updated manuscript. stuff

\end{document}
